Scheduling and Vectorization for MPC

### 2022-02-27 paper_SIMD.tex
Improved Extension of Baisic Vectorization with Array Writes.

\subsection{Towards Extension of Basic Vectorization}

@@

\begin{algorithmic}
\STATE for i in range(N):
\STATE \hspace{0.25cm} A[i] = B[i] + 10;
\STATE \hspace{0.25cm} B[i] = A[i] * D[i-1];
\STATE \hspace{0.25cm} C[i] = A[i] * D[i-1];
\STATE \hspace{0.25cm} D[i] = B[i] * C[i];
\end{algorithmic}

@@

\begin{algorithmic}
\STATE for i in range(N):
\STATE 1. $\texttt{A}_0$ = $\phi(\texttt{A},\texttt{A}_1)$
\STATE 2. $\texttt{B}_0$ = $\phi(\texttt{B},\texttt{B}_1)$
\STATE 3. $\texttt{C}_0$ = $\phi(\texttt{C},\texttt{C}_1)$
\STATE 4. $\texttt{D}_0$ = $\phi(\texttt{D},\texttt{D}_1)$
\STATE 5. $\texttt{A}_1$ = $\texttt{A}_0$; $\texttt{A}_1$[i] = $\texttt{B}_0$[i] + 10; \COMMENT{equiv. to Update}
\STATE 6. $\texttt{B}_1$ = $\texttt{B}_0$; $\texttt{B}_1$[i] = $\texttt{A}_1$[i] * $\texttt{D}_0$[i-1];
\STATE 7. $\texttt{C}_1$ = $\texttt{C}_0$; $\texttt{C}_1$[i] = $\texttt{A}_1$[i] * $\texttt{D}_0$[i-1];
\STATE 8. $\texttt{D}_1$ = $\texttt{D}_0$; $\texttt{D}_1$[i] = $\texttt{B}_1$[i] * $\texttt{C}_1$[i];
\end{algorithmic}

There is a cycle around $\texttt{B}_0$ = $\phi(\texttt{B},\texttt{B}_1)$ that includes statement $\texttt{A}_1$[i] = $\texttt{B}_0$[i] + 10;
and that statement won't be vectorized even though in fact there is no loop-carried dependency from the write of $\texttt{B}_1$[i] at 8 to the
read of $ ... = \texttt{B}_0$[i] at 6.

@@

Consider the earlier example. There is a single loop, $i$. Clearly, there is no pair $\underline{i}$ and $\underline{i}'$, where $\underline{i} < \underline{i}'$ that make $\underline{i} = \underline{i}'$ (due to the def-use pairs of \texttt{A} 6-8 and 6-10).
Therefore, we remove the back edge from 6 to 1. Analogously, we remove the back edges from 8 to 2 and 10 to 3. However, there are many values $\underline{i} < \underline{i'}$ that make $\underline{i} = \underline{i'}-1$ and the back edge from 12 to 4 remains (def-use pairs for \texttt{D}). As a result of removing these spurious edges, Basic Vectorization will find that statement 6 is vectorizable. Statements 8, 10 and 12 will correctly appear in the FOR loop.

@@

\ana{TODO: I think we should implement this.}

@@

\subsection{Extension of Basic Vectorization with Array Writes}

@@

For now, we restrict array updates to \emph{canonical updates}. Assume (for simplicity) a two-dimensional array $\texttt{A}[I,J]$. A canonical update is the following:
\begin{algorithmic}
\STATE for i in range(I):
\STATE \hspace{0.25cm} for j in range(J):
\STATE \hspace{0.55cm} ...
\STATE \hspace{0.55cm} A[i,j] = ...
\STATE \hspace{0.55cm} ...
\end{algorithmic}

The update $\texttt{A}[i,j]$ can be nested into an inner loop and there may be multiple updates, i.e., writes to $\texttt{A}[i,j]$. However, update such as $\texttt{A}[i-1,j] = ...$ or $\texttt{A}[i-1,j-1] = ...$, etc., is not allowed. Additionally, while there could be several different loops that perform canonical updates, they must be of the same dimensionality, i.e., an update of higher or lower dimension, e.g., $A[i,j,k] = ...$ is not allowed. We compute the \emph{canonical dimensionality} of each write array in the obvious way \emph{before basic vectorization}. This restriction simplifies reasoning in this early stage of the compiler; we will look to relax the restriction in future work.

@@

Reads through an arbitrary formula, such as $\texttt{A}[i-1]$ for example, are allowed; currently, our projection function returns dummy values if the read formula is out of bounds; we assume the programmer ensures that the program still computes correct output in this case.

@@

There are two changes to Basic Vectorization to account for write arrays. We can account for them during processing of raise dimension/drop dimension in Phase 1 of Basic Vectorization.

One change to Basic vectorization is the expansion of dimension if the array write or read occurs in a nested loop. That is, if there is an update $\texttt{A}[i,j] = ...$ that occurs in loop dimensionality $i,j,k$, $\texttt{A}[i,j]$ will be rewritten into $\texttt{A}[i,j,k]$. Similarly, a read $\texttt{A}[f(i,j)]$ will be rewritten into $\texttt{A}[f(i,j),k]$. ($\texttt{A}[f(i,j),k]$ will be reshaped as $f(i,j)*I*J+k$ during Phase 1 of Basic Vectorization. \ana{TODO: Double check.})

The other change concerns def-use edges $X \rightarrow Y$ where $X$ defines and $Y$ uses an array variable. The definition can be an update $A_2 = update(A_1,...)$ or a pseudo $\phi$-node $A_2 = \phi(A_0,A_1)$. Note that $\phi$ nodes for arrays are no subscript operations on those $\phi$-nodes the way there are in scalar arrays. These edges are not handled in the same way as in Basic Vectorization, specifically, we do not raise and drop dimension as we do for scalars in Basic Vectorization. A key invariant is that the dimension of an array $A$ cannot go above or drop below $A$'s canonical dimensionality. We enumerate the cases of def-use edges.

@@

First, the canonical dimensionality of all \texttt{A,B,C} and \texttt{D} is 1. 
Thus, there is no addition of extra dimension for inner loops. After Phase 1 
of Basic Vectorization the Aiken's array write example will be (roughly) as follows:

\begin{algorithmic}
\STATE for i in range(N):
\STATE 1. $\texttt{A}_1$ = $\phi(\texttt{A}_0,\texttt{A}_2)$
\STATE 2. $\texttt{B}_1$ = $\phi(\texttt{B}_0,\texttt{B}_2)$
\STATE 3. $\texttt{C}_1$ = $\phi(\texttt{C}_0,\texttt{C}_2)$
\STATE 4. $\texttt{D}_1$ = $\phi(\texttt{D}_0,\texttt{D}_2)$
\STATE 5. $\texttt{A}_2 = update(\texttt{A}_1, \stackrel{\rightarrow}{i}, \texttt{B}_1[\stackrel{\rightarrow}{i}] + 10)$;
\STATE 6. $\texttt{B}_2 = update(\texttt{B}_1, \stackrel{\rightarrow}{i}, \texttt{A}_2[\stackrel{\rightarrow}{i}] * \texttt{D}_1[\stackrel{\rightarrow}{i-1}])$;
\STATE 7. $\texttt{C}_2 = update(\texttt{C}_1, \stackrel{\rightarrow}{i}, \texttt{A}_2[\stackrel{\rightarrow}{i}] * \texttt{D}_1[\stackrel{\rightarrow}{i-1}])$;
\STATE 8. $\texttt{D}_2 = update(\texttt{D}_1; \stackrel{\rightarrow}{i}, \texttt{B}_2[\stackrel{\rightarrow}{i}] * \texttt{C}_2[\stackrel{\rightarrow}{i}])$;
\end{algorithmic}

Phase 2 computes the closure of 4; $cl = \{4,6,7, 8\}$ 
while 5 is vectorizable. Recall that 1,2, and 3 are targetless phi-nodes. Since the closure $cl$ includes updates to $B$ and $C$,
the corresponding phi-nodes are added to the closure, i.e., the FOR loop. The uses of $A_1$ and $B_1$ in the vectorized statement
turn into uses of $A_0$ and $B_0$ respectively. (But note that $A_0$ is irrelevant; the updates writes into array $A_2$ in parallel.)

\begin{algorithmic}
\STATE 1. $\texttt{A}_2 = update(\texttt{A}_0; \stackrel{\rightarrow}{i}, \mathit{ADD\_SIMD}(\texttt{B}_0[\stackrel{\rightarrow}i],[10,...])$ \COMMENT{Fully vectorized, size N.}
\STATE FOR i=0; i<N; i++; \COMMENT{ MOTION loop }
\STATE 2. $\texttt{B}_1$ = $\phi(\texttt{B}_0,\texttt{B}_2)$
\STATE 3. $\texttt{C}_1$ = $\phi(\texttt{C}_0,\texttt{C}_2)$
\STATE 4. $\texttt{D}_1$ = $\phi(\texttt{D}_0,\texttt{D}_2)$
\STATE 5. $\texttt{B}_2 = update(\texttt{B}_1, i, \mathit{MUL}(\texttt{A}_2[i], \texttt{D}_1[{i-1}])$
\STATE 6. $\texttt{C}_2 = update(\texttt{C}_1, i, \mathit{MUL}(\texttt{A}_2[i], \texttt{D}_1[{i-1}])$
\STATE 7. $\texttt{D}_2 = update(\texttt{D}_1, i, \mathit{MUL}(\texttt{B}_2[i], \texttt{C}_1[i])$
\end{algorithmic}

\ana{TODO: Format either Histogram or Matrix Multiplication. Both are interesting examples that use output arrays.}

>>>>

\subsection{Extension of Basic Vectorization}

@@

\begin{verbatim}
for i in range(N):
  A[i] = B[i] + 10;
  B[i] = A[i] * D[i-1];
  C[i] = A[i] * D[i-1];
  D[i] = B[i] * C[i];
\end{verbatim}

@@

\begin{verbatim}
for i in range(N):
1. A_1 = PHI(A_0,A_2)
2. B_1 = PHI(B_0,B_2)
3. C_1 = PHI(C_0,C_2)
4. D_1 = PHI(D_0,D_2)
5. A_2 = update(A_1, i, B_1[i] + 10); 
6. B_2 = update(B_1, i, A_2[i] * D_1[i-1]);
7. C_2 = update(C_1, i, A_2[i] * D_1[i-1]);
8. D_2 = update(D_1, i, B_2[i] * C_2[i]);
\end{verbatim}

\begin{comment}
\begin{algorithmic}
\STATE for i in range(N):
\STATE \hspace{0.25cm} A[i] = B[i] + 10;
\STATE \hspace{0.25cm} B[i] = A[i] * D[i-1];
\STATE \hspace{0.25cm} C[i] = A[i] * D[i-1];
\STATE \hspace{0.25cm} D[i] = B[i] * C[i];
\end{algorithmic}

\begin{algorithmic}
\STATE for i in range(N):
\STATE 1. $\texttt{A}_0$ = $\phi(\texttt{A},\texttt{A}_1)$
\STATE 2. $\texttt{B}_0$ = $\phi(\texttt{B},\texttt{B}_1)$
\STATE 3. $\texttt{C}_0$ = $\phi(\texttt{C},\texttt{C}_1)$
\STATE 4. $\texttt{D}_0$ = $\phi(\texttt{D},\texttt{D}_1)$
\STATE 5. $\texttt{A}_1$ = $\texttt{A}_0$; $\texttt{A}_1$[i] = $\texttt{B}_0$[i] + 10; \COMMENT{equiv. to Update}
\STATE 6. $\texttt{B}_1$ = $\texttt{B}_0$; $\texttt{B}_1$[i] = $\texttt{A}_1$[i] * $\texttt{D}_0$[i-1];
\STATE 7. $\texttt{C}_1$ = $\texttt{C}_0$; $\texttt{C}_1$[i] = $\texttt{A}_1$[i] * $\texttt{D}_0$[i-1];
\STATE 8. $\texttt{D}_1$ = $\texttt{D}_0$; $\texttt{D}_1$[i] = $\texttt{B}_1$[i] * $\texttt{C}_1$[i];
\end{algorithmic}
\end{comment}

There is a cycle around \texttt{B\_1 = PHI(B\_0,B\_2)} that includes statement 
\texttt{A\_1 = update(A\_0, i, B\_1[i] + 10)} and that statement won't be vectorized even 
though in fact there is no loop-carried dependency from the write of \texttt{B\_1[i]} at 6 to the
read of \texttt{ ... = B\_1[i]} at 8.

@@

Consider the earlier example. There is a single loop, $i$. Clearly, there is no pair $\underline{i}$ and $\underline{i}'$, where $\underline{i} < \underline{i}'$ that make $\underline{i} = \underline{i}'$ 
due to the def-use pairs of \texttt{A} 5-6 and 5-7.
Therefore, we remove the back edge from 5 to the phi-node 1. Analogously, we remove the back edges from 6 to 2 and from 7 to 3. However, there are many values $\underline{i} < \underline{i'}$ that make $\underline{i} = \underline{i'}-1$ and the back edge from 8 to 4 remains (def-use pairs for \texttt{D}). As a result of removing these spurious edges, Basic Vectorization will find that statement 5 is vectorizable. Statements 6, 7 and 8 will correctly appear in the FOR loop.

Note however, that this step renders some array phi-nodes target-less. We handle target-less phi-nodes with a minor extension of Basic Vectorization. 
First, we merge closures that update the same array. \ana{Why, intuition?} Second, we add the target-less node of array \texttt{A} back to the closure that updates \texttt{A} ---
the intuition is, even if there is no loop-carried dependence from writes to reads on \texttt{A}, \texttt{A} is written and the write (i.e., update) cannot be vectorized; 
therefore, the updated array has to carry to the next iteration of the loop. Third, in cases when the phi-node remains target-less, i.e., cases when the
array write can be vectorized, we have to properly remove the phi-node replacing uses of the left-hand side of the phi-node with its arguments.

@@

\ana{TODO: WIP, get to BV without MUX refinement for now? For now, skip MUX refinement.}

@@

@@

For now, we restrict array updates to \emph{canonical updates}. Assume (for simplicity) a two-dimensional array \texttt{A[I,J]}. A canonical update is the following:
\begin{verbatim}
for i in range(I):
  for j in range(J):
    ...
    A[i,j] = ...
    ...
\end{verbatim}

The update \texttt{A[i,j]} can be nested into an inner loop and there may be multiple updates, i.e., writes to \texttt{A[i,j]}. However, update such as \texttt{A[i-1,j] = ...} or \texttt{A[i-1,j-1] = ...}, etc., is not allowed. Additionally, while there could be several different loops that perform canonical updates, they must be of the same dimensionality, i.e., an update of higher or lower dimension, e.g., \texttt{A[i,j,k] = ...} is not allowed. We compute the \emph{canonical dimensionality} of each write array by examining the array writes in the original program and rejecting programs that violate the canonical write restriction. This restriction simplifies reasoning in this early stage of the compiler; we will look to relax the restriction in future work.

@@

Reads through an arbitrary formula, such as \texttt{A[i-1]} for example, are allowed; currently, the projection function returns dummy values if the read formula is out of bounds; we assume the programmer ensures that the program still computes correct output in this case.

@@

\begin{comment}
There are two changes to Basic Vectorization to account for write arrays. We can account for them during processing of raise dimension/drop dimension in Phase 1 of Basic Vectorization.

One change to Basic vectorization is the expansion of dimension if the array write or read occurs in a nested loop. That is, if there is an update $\texttt{A}[i,j] = ...$ that occurs in loop dimensionality $i,j,k$, $\texttt{A}[i,j]$ will be rewritten into $\texttt{A}[i,j,k]$. Similarly, a read $\texttt{A}[f(i,j)]$ will be rewritten into $\texttt{A}[f(i,j),k]$. ($\texttt{A}[f(i,j),k]$ will be reshaped as $f(i,j)*I*J+k$ during Phase 1 of Basic Vectorization. \ana{TODO: Double check.}) 
\end{comment}

In addition to the changes for the handling of target-less phi-nodes, Basic Vectorization has to handle differently def-use edges $X \rightarrow Y$ where $X$ defines and $Y$ uses an array variable. The definition can be an update \texttt{A\_2 = update(A\_1,i,...)} or a pseudo $\phi$-node \texttt{A\_2 = PHI(A\_0,A\_1)}, etc.. Note that $\phi$-nodes for arrays have no subscript operations the way there are subscript operations in analysis-introduced arrays representing scalars. In addition, array variables are different from scalar variables. Raising and dropping dimension still apply, however, the dimension cannot be raised or dropped to a dimension lower than the canonical one:

@@

First, the canonical dimensionality of all \texttt{A,B,C} and \texttt{D} is 1. 
After Phase 1 of Basic Vectorization the Aiken's array write example will be (roughly) as follows:

\begin{verbatim}
for i in range(N):
1. A_1 = PHI(A_0,A_2)
2. B_1 = PHI(B_0,B_2)
3. C_1 = PHI(C_0,C_2)
4. D_1 = PHI(D_0,D_2)
5. A_2 = update(A_1, I, B_1[I] + 10); 
6. B_2 = update(B_1, I, A_2[I] * D_1[I-1]);
7. C_2 = update(C_1, I, A_2[I] * D_1[I-1]);
8. D_2 = update(D_1, I, B_2[I] * C_2[I]);
\end{verbatim}

Note that since all def-uses are same-level (i.e., reads and writes of the array elements) 
no raise dimension or drop dimension happens.

\begin{comment}
\begin{algorithmic}
\STATE for i in range(N):
\STATE 1. $\texttt{A}_1$ = $\phi(\texttt{A}_0,\texttt{A}_2)$
\STATE 2. $\texttt{B}_1$ = $\phi(\texttt{B}_0,\texttt{B}_2)$
\STATE 3. $\texttt{C}_1$ = $\phi(\texttt{C}_0,\texttt{C}_2)$
\STATE 4. $\texttt{D}_1$ = $\phi(\texttt{D}_0,\texttt{D}_2)$
\STATE 5. $\texttt{A}_2 = update(\texttt{A}_1, \stackrel{\rightarrow}{i}, \texttt{B}_1[\stackrel{\rightarrow}{i}] + 10)$;
\STATE 6. $\texttt{B}_2 = update(\texttt{B}_1, \stackrel{\rightarrow}{i}, \texttt{A}_2[\stackrel{\rightarrow}{i}] * \texttt{D}_1[\stackrel{\rightarrow}{i-1}])$;
\STATE 7. $\texttt{C}_2 = update(\texttt{C}_1, \stackrel{\rightarrow}{i}, \texttt{A}_2[\stackrel{\rightarrow}{i}] * \texttt{D}_1[\stackrel{\rightarrow}{i-1}])$;
\STATE 8. $\texttt{D}_2 = update(\texttt{D}_1; \stackrel{\rightarrow}{i}, \texttt{B}_2[\stackrel{\rightarrow}{i}] * \texttt{C}_2[\stackrel{\rightarrow}{i}])$;
\end{algorithmic}
\end{comment}

Phase 2 computes the closure of 4; $cl = \{4,6,7, 8\}$ 
while 5 is vectorizable. Recall that 1,2, and 3 are target-less phi-nodes. Since the closure $cl$ includes updates to \texttt{B} and \texttt{C},
the corresponding phi-nodes are added back to the closure and the def-use edges are added back to the target-less nodes. The uses of \texttt{A\_1} and \texttt{B\_1} in the vectorized statement
turn into uses of \texttt{A\_0} and \texttt{B\_0} respectively; this is done for all original target-less phi-node. (But note that \texttt{A\_0} is irrelevant; the update writes into array \texttt{A\_2} in parallel.)
Finally, the target-less phi-node for \texttt{A} is discarded.

\begin{verbatim}
1. A_2 = update(A_0, I, ADD_SIMD(B_0[I],10));
   equiv. to A_2[I] = ADD_SIMD(B_0[I],10)
FOR i=0; i<N; i++; // MOTION loop
2. B_1 = PHI(B_0,B_2)
3. C_1 = PHI(C_0,C_2)
4. D_1 = PHI(D_0,D_2)
5. B_2 = update(B_1, i, A_2[i] * D_1[i-1]);
   equiv. to B_2 = B_1; B_2[i] = A_2[i] * D_1[i-1];
6. C_2 = update(C_1, i, A_2[i] * D_1[i-1]);
7. D_2 = update(D_1, i, B_2[i] * C_2[i]);
\end{verbatim}

\begin{comment}
\begin{algorithmic}
\STATE 1. $\texttt{A}_2 = update(\texttt{A}_0; \stackrel{\rightarrow}{i}, \mathit{ADD\_SIMD}(\texttt{B}_0[\stackrel{\rightarrow}i],[10,...])$ \COMMENT{Fully vectorized, size N.}
\STATE FOR i=0; i<N; i++; \COMMENT{ MOTION loop }
\STATE 2. $\texttt{B}_1$ = $\phi(\texttt{B}_0,\texttt{B}_2)$
\STATE 3. $\texttt{C}_1$ = $\phi(\texttt{C}_0,\texttt{C}_2)$
\STATE 4. $\texttt{D}_1$ = $\phi(\texttt{D}_0,\texttt{D}_2)$
\STATE 5. $\texttt{B}_2 = update(\texttt{B}_1, i, \mathit{MUL}(\texttt{A}_2[i], \texttt{D}_1[{i-1}])$
\STATE 6. $\texttt{C}_2 = update(\texttt{C}_1, i, \mathit{MUL}(\texttt{A}_2[i], \texttt{D}_1[{i-1}])$
\STATE 7. $\texttt{D}_2 = update(\texttt{D}_1, i, \mathit{MUL}(\texttt{B}_2[i], \texttt{C}_1[i])$
\end{algorithmic}
\end{comment}

\paragraph{Example 2} Now consider the MPC Source of Histogram:

\begin{verbatim}
for i in range(0, num_bins):
   res1 = PHI(res, res2)
   for j in range(0, N):
      res2 = PHI(res1, res3)
      tmp1 = (A[j] == i)
      tmp2 = (res2[i] + B[j])
      tmp3 = MUX(tmp1, res2[i], tmp2)
      res3 = Update(res2, i, tmp3)     
return res1
\end{verbatim}

The canonical dimensionality of \texttt{res} is 1. Also, the phi-node \texttt{res2 = PHI(res1, res3)} is a target-less phi-node (the implication being that the inner for loop can be vectorized across $i$). After Phase 1, Basic vectorization produces the following (everything is implicitly vectorized along $i$ and $j$ and the update is turned into a regular write):

\begin{verbatim}
A1 = raise_dim(A, j, ((i:num_bins),(j:N)))
B1 = raise_dim(B, j, ((i:num_bins),(j:N)))
I = raise_dim(i, ((i:num_bins),(j:N)))
for i in range(0, num_bins):
   res1 = PHI(res, res2) // target-less, no drop_dim
   res1' = raise_dim(res1, (j:N))
   for j in range(0, N):
      res2 = PHI(res1', res3)
      tmp1 = (A1 == I)
      tmp2 = (res2 + B1)
      tmp3 = MUX(tmp1, res2, tmp2)
      res3 = res2 // copy propagation: res2 into res3
      res3 = tmp3 // "normal": res3[I,J] = tmp3[I,J]    
return res1
\end{verbatim}

Processing the inner loop in Phase 2 vectorizes \texttt{tmp1 = (A1 == I)} along the $j$ dimension but leaves the rest of the statements in a MOTION loop. Processing the outer loop is interesting. This is because the PHI node is a target-less node, and therefore, there are no closures! Thus everything can be vectorized along the $i$ dimension:

\begin{verbatim}
A1 = raise_dim(A, j, ((i:num_bins),(j:N)))
B1 = raise_dim(B, j, ((i:num_bins),(j:N)))
I1 = raise_dim(i, ((i:num_bins),(j:N)))

tmp1[I,J] = (A1[I,J] == I1[I,J])

res1' = raise_dim(res, (j:N)) // raising original array to a 2-dimensional array
for j in range(0, N):
   res2 = PHI(res1', res3)
   tmp2[I,j] = (res2[I,j] + B1[I,j])
   tmp3[I,j] = MUX(tmp1[I,j], res2[I,j], tmp2[I,j])
   res3 = res2
   res3[I,j] = tmp3[I,j]
res1 = drop_dim(res2) // Have to add drop_dim before removing redundant phi-node      
return res1
\end{verbatim}

The cleanup phase can then get rid of $j$ in the res variables and tmp variables, so the loop operates over the num\_bins-size vectors. 
This will lead to dropping raise\_dim and drop\_dim as well:

\begin{verbatim}
A1 = raise_dim(A, j, ((i:num_bins),(j:N)))
B1 = raise_dim(B, j, ((i:num_bins),(j:N)))
I1 = raise_dim(i, ((i:num_bins),(j:N)))

tmp1[I,J] = (A1[I,J] == I1[I,J])

for j in range(0, N):
   res2 = PHI(res1', res3) // now 1-dim array
   tmp2[I] = (res2[I] + B1[I,j])
   tmp3[I] = MUX(tmp1[I,j], res2[I], tmp2[I])
   res3 = res2
   res3[I] = tmp3[I]
return res2
\end{verbatim}
